Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-04 paper/main.tex
Some changes by Kumar

% Broad summary of your work, come to your problem definition.

@@

\label{section2}

For a MIMO-OFDM system with $N_T$ transmitter and $N_R$ receiver antennas, each subcarrier $i$ with time instant $t$ could be modelled as a flat-fading MIMO channel. This flat-fading MIMO channel could be modelled as

\vspace{-1pt}

\begin{equation}
\by_{i,t} = \bH_{i,t} \bx_{i,t}+ \bf{\eta_{i,t}}
\end{equation}

\vspace{-1pt}

where the channel matrix $\bH_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $\bx_{i,t} \in \mathbb{C}^{N_T}$; the output $\by_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $\bH_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_R}$, $\Sigma_{i,t} \in \mathbb{C}^{N_R \times N_R}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_R}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

@@

\subsection{Scalar Parameterization}
\label{givens}

The degrees of freedom in the spatial information matrix is much smaller than the number of real entries in the matrix because of the geometrical structure between the columns of the matrix \cite{4114278}. An orthonormal matrix with $t$ rows and $n$ columns can be represented as

@@

where $D_{k}$ is the diagonal matrix given as $D_{k}\big(\phi_{k,k}, \ldots, \phi_{k,t} \big)$ =  $diag\big( 1_{k-1}, e^{j\phi_{k,k}},\ldots, e^{j\phi_{k,t}}  \big)$, $1_{k-1}$ is (k-1) ones; and t x n matrix $\tilde{I}$ = $\big[I_{n}, 0_{n,t-n}\big]^{T}$. The Givens matrix \textbf{G} is given as

@@

I_{m-2} & & & \\
& \cos\;\theta & - \sin\;\theta & \\
& \sin\;\theta & \cos\;\theta & \\
& & & I_{t-m}

@@

\begin{equation}
p(\theta) = 2l\sin(\theta)^{2l-1}\cos(\theta), \theta \in [0, \frac{\pi}{2}), for \; l = 1,2,\ldots,t-1
\end{equation}

Here all $\theta_i$ and $\phi_i$ are statistically independent which is usefel for tracking them across time as explained in the next subsection. The total number of parameters obtained from the decomposition of a complex orthogonal matrix $N_{T} \times N_{R} $ is given by the relation $N_{R}(2N_{T} - N_{R}) $ \cite{4114278}. Number of $\phi = N_{R}(2N_{T} - N_{R}-1)/2$ while the number of $\theta = N_{T}(2N_{T} - N_{R}+1)/2$

% may cross pi and come immediately to -pi, therefore, values are unwrapped while calculating them. Unwrapping is performed at the receiver over the frequency initially and later in time.

@@

%Explain prediction and quantization steps here itself ! (succintly)

\section{SIMULATION AND DISCUSSION}
\label{section3}

>>>>

In this paper, we propose a method for predictive quantization in the time domain over the subcarriers of a MIMO-OFDM system using scalar parameters. We also exploit the joint time-frequency correlation of these scalar parameters on the transmitter side. TODO how we solve it?

The rest of this paper is organized as follows: Section~\ref{section2}, we start by explaining the system model and the method for scalar quantization \& interpolation of the precoder matrix. In \ref{section3}, we perform various simulations for our approach and show the benefits from the improved BER rates and Achievable Rate.
%Since $H=U\Sigma V$, it is sufficient to quantize V*(precoder) and send this information back. In an OFDM channel, this data consume significant amount of bits and therefore, sending the complete data could consume too much bandwidth data. For e.g. an OFDM channel with 4 transmitters, 2 receiver antennas, and 64 subcarriers would require 64*(no. of bits required to send one precoder ~ 12-16 bits) ~ 896 bits per frame. This information could be significantly reduced if we provide better quantization and interpolation techniques/strategies. Also, the matrices which need to be fed back could be broken down into independent scalar parameters. These scalar quantities could be later quantized and interpolated.
% Broad summary of your work, come to your problem definition.

@@

\label{section2}
\begin{equation}
\by_{i,t} = \bH_{i,t} \bx_{i,t}+ \bf{\eta_{i,t}}
\end{equation}
where the channel matrix $H_{i,t} \in \mathbb{C}^{N_R \times N_T}$; the input $x_{i,t} \in \mathbb{C}^{N_T}$; the output $y_{i,t} \in \mathbb{C}^{N_R}$ and $\eta$ is the complex additive white gaussian noise vector with distribution $\tilde{\mathcal{N}}(0,I_{N_R})$. On applying thin SVD to H, we get $H_{i,t} = U_{i,t} \Sigma_{i,t} V_{i,t}^{H}$, where $U_{i,t} \in \mathbb{C}^{N_R \times N_T}$, $\Sigma_{i,t} \in \mathbb{C}^{N_T \times N_T}$  and $V_{i,t} \in \mathbb{C}^{N_T \times N_T}$. $U_{i,t}$ and $V_{i,t}$ are orthonormal column matrices and $\Sigma_{i,t}$ contains the singular values $\sigma_1 \geq \ldots \geq \sigma_{N_T} > 0$ of H. The entries of H are assumed to be i.i.d. $\tilde{\mathcal{N}}(0,1)$, complex circularly symmetric Gaussian with mean zero and variance 1. Therefore, the first n column vectors of $V_{i,t}$ have to be quantized and fed back to the transmitter as channel spatial information.

@@

\subsection{Scalar Paramatrization}
\label{givens}
The degrees of freedom in the spatial information matrix is much smaller than the number of real entries in the matrix because of the geometrical structure between the columns of the matrix~\cite{4114278}. An orthonormal matrix with $t$ rows and $n$ columns can be represented as

@@

where $D_{k}$ is the diagonal matrix given as $D_{k}\big(\phi_{k,k}, \ldots, \phi_{k,t} \big)$ =  $\mbox{diag}\big( 1_{k-1}, e^{j\phi_{k,k}},\ldots, e^{j\phi_{k,t}}  \big)$, $1_{k-1}$ is (k-1) ones; and t x n matrix $\tilde{I}$ = $\big[I_{n}, 0_{n,t-n}\big]^{T}$. The Givens matrix \textbf{G} is given as

@@

I_{m-2} & & & \\
& \cos\theta & -\sin\theta & \\
& \sin\theta & \cos\theta & \\
& & & I_{t-m}

@@

%TODO What is t in the equation below?
\begin{equation}
p(\theta) = 2l(\sin\theta)^{2l-1}\cos\theta, \theta \in \left[0, \frac{\pi}{2}\right) \mbox{ for } l = 1,2,\ldots,t-1
\end{equation}
Here all $\theta_i$ and $\phi_i$ are statistically independent, making it useful for tracking them across time as explained in the next subsection. The total number of parameters obtained from the decomposition of a complex orthogonal matrix $N_{T} \times N_{R} $ is $N_{R}(2N_{T} - N_{R})$~\cite{4114278}. The number of $\phi_i$ parameters is $N_{R}(2N_{T} - N_{R}-1)/2$ while the number of $\theta$ parameters is $N_{T}(2N_{T} - N_{R}+1)/2$.
% may cross pi and come immediately to -pi, therefore, values are unwrapped while calculating them. Unwrapping is performed at the receiver over the frequency initially and later in time.

@@

%Explain prediction and quantization steps here itself ! (succintly)
\section{Simulation and discussion}
\label{section3}
